\chapter{Where to Go from Here?}

After completing this entire book you should have a very good understanding of
the essential features of \SB{} and \cocos{}. However, each type of game has its
own challenges. Additional books and tutorials will help you understand the
structure of different types of games.

Note that all of the resources listed here are written in the Objective-C
language. This book is (to my knowledge) currently the only book that uses
Swift.

\section{Building Games with the Physics Engine}
There two different resources I would recommend:

\begin{description}
\item[Make School's Peeved Penguins Tutorial] This tutorial provides an
introduction to \SB{} by cloning the popular game \textit{Angry Birds}. It uses
the physics engine to build the game. Link:
\url{https://www.makeschool.com/tutorials/getting-started-with-spritebuilder/}
\item[Learn SpriteBuilder Book] This is another book that focuses on \SB{}.
However, it uses a physics based game throughout the entire book. Link:
\url{http://www.apress.com/9781484202630}
\end{description}

\section{Building Puzzle Games}

\begin{description}
\item[Make School's 2048 Tutorial] If you are interested in using \SB{} and \cocos{} to build a puzzle game, you
should check out Make School's 2048 tutorial. Link:
\url{https://www.makeschool.com/tutorials/build-your-own-2048-with-spritebuilder-and-cocos2d/part-1}
\end{description}

\section{Getting Help}

\begin{description}
\item[SpriteBuilder forum] Folks on the \SB{} forum have been extremely helpful
in the past. If you get stuck during a tutorial or while building your own
game, you should ask for help there. Link:
\url{https://forum.spritebuilder.com}
\end{description}

\section{Build your own Game!}
I hope this book has helped you to learn enough about \SB{} and \cocos{} to get
started on your own game. If you finish a project, I would love to hear from
you at: \textit{me@benjamin-encz.de}!
